Proposed Solution

### 2016-11-13 Ennan-Proposal/related.tex
Grammar

We now position our work to already existing work. Most of the 
work falls into, what is traditionally considered, system's research.

@@

Compared with these existing efforts, 
our work mainly focused on software systems, \eg, MySQL and Apache,
rather than network configurations. In addition, we do not need 
the user of \app to manually write a configuration file with the proposed
language, since \app can automatically parse a target configuration
file into our proposed representation.

We previously discussed ConfValley by Huang {\em et al.} proposed a specification for configuration validation%
~\cite{huang15confvalley}.

@@

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore}.
EnCore~\cite{zhang14encore} is the work closest to \app.
It introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interest.
In this way, EnCore filters out irrelevant information and reduces
false positives; moreover, the templates are able to express
system environment information that other machine learning
techniques cannot handle.
Compared to EnCore, \app has the following advantages.
Firstly, \app does not rely on 100\% correctness in the files of the given configuration set. 
Secondly, \app not only covers many more types of 
misconfigurations, but also introduces probabilistic types.
Finally, \app is a language framework, which can 
even be used to write configuration files, but EnCore is only a 
misconfiguration detection tool.

@@

\paragraph{Misconfiguration tolerance.}
There have been several efforts proposed to test whether systems are 
tolerant to misconfigurations~\cite{xu13do}. 
%ConfErr~\cite{} uses a human error hodel from psychology and
%linguistics to inject misconfigurations into systems.
SPEX~\cite{xu13do} takes a white-box testing approach to automatically
extract configuration parameter constraints from source code and generates 
misconfigurations to test whether systems can tolerate potential
configuration errors.

>>>>

We will now compare our work to existing work. Most of this 
work falls into what is traditionally considered system's research.

@@

Compared with these existing efforts, 
our work is mainly focused on software systems, \eg, MySQL and Apache,
rather than network configurations. In addition, we do not need 
the user of \app to manually write a configuration file with the proposed
language, since \app can automatically parse a target configuration
file into our proposed representation.

We previously discussed ConfValley by Huang {\em et al.}, which proposed a specification for configuration validation%
~\cite{huang15confvalley}.

@@

Several machine learning-based misconfiguration detection efforts 
have been proposed~\cite{yuan11context, zhang14encore}.
EnCore~\cite{zhang14encore} is the work closest to \app.
It introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that force learning to focus on patterns of interest.
In this way, EnCore filters out irrelevant information and reduces
false positives; moreover, the templates are able to express
system environment information that other machine learning
techniques cannot handle.
Compared to EnCore, \app has the following advantages.
Firstly, \app does not rely on 100\% correctness in the files of the given configuration set. 
Secondly, \app not only covers many more types of 
misconfigurations, but also introduces probabilistic types.
Finally, \app is a language framework, which can 
even be used to write configuration files, whereas EnCore is only a 
misconfiguration detection tool.

@@

\paragraph{Misconfiguration tolerance.}
There have been several efforts proposed to test whether systems are 
tolerant to misconfigurations~\cite{xu13do}. 
%ConfErr~\cite{} uses a human error hodel from psychology and
%linguistics to inject misconfigurations into systems.
SPEX~\cite{xu13do} takes a white-box testing approach to automatically
extract configuration parameter constraints from source code, and generates 
misconfigurations to test whether systems can tolerate potential
configuration errors.

### 2016-11-13 Ennan-Proposal/solutions.tex
Grammar

We now describe a formalism how to compute the set of learned
probabilistic rules, denoted with $\mathcal{PR}$.
With $\mathcal{U}$ we denote a set of configuration files in the 
intermediate representation. If a template can be instantiated with
keywords from file $f$ and the obtained rule $r$ holds, we state that with the predicate 
$\mathit{appears}(r,f)$.
If a template is instantiated and we obtain rule $r$, with  the predicate 
$\mathit{holds}(r,f)$ we state that either $\mathit{appears}(r,f)$ holds, or $r$ could not be instantiated with keywords from $f$. With every 
rule $r$ we define two sets:
\begin{align*}
S_A(r)& =\{ \ f \in \mathcal{U}\ | \ \mathit{appears}(r,f)\  \} \\
S_H(r)& =\{ \ f \in \mathcal{U}\  | \ \mathit{holds}(r,f) \ \}
\end{align*}
We define then set $\mathcal{PR}$ as
$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)| > T_2 \ \} $$
where $T_1$ is a threshold value for considering rules which are true in 
majority of cases, and $T_2$ is a threshold value for considering rules 
for which we have at least some examples that that rule is will 
appear in the files. Finding the exact values of $T_1$ and $T_2$ is 
and their connection to $|\mathcal{U}|$
is a question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $T_1$ and $T_2$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.

Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabeled and seeks to discover some hidden underlying structure.
Although our set is also unlabeled, we make the assumption that some majority of the training set must be correct for their biggest part.
We are again learning a model which will provide clear justification (error locations) for the classification.
However, with this approach we will not have the formal guarantees of the ConfigC approach.
From previous work, we believe this is a worthwhile trade-off in order to decrease the fasle positive rate.

@@

In addition to checking for correlation, type- or ordering errors, 
the user may also want to examine if there are anomalous values that 
a keyword is assigned to. Such errors may also cause tricky and critical performance issues that are hard to debug.
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.

We now describe a technique that we plan to 
explore to detect anomalous values for 
numerical attributes. Let $A$ be the set of attributes contained in the 
configuration files in the sample dataset. 
Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
values corresponding to attribute $a$, seen over the entire sample dataset.
For each $v_a$, we compute 
an interval  $$[\hat{v_a} - 50*MAD(v_a), \hat{v_a} + 50*MAD(v_a)],$$ 
where $\hat{v_a}$ represents the median over the values 
in $v_a$ and $MAD(v_a$) refers to the 
median absolute deviation. 
This is a variant of a standard outlier detection test, namely the Hampel identifier. (Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
for a normal distribution.) 
In the checking phase, as long as the checker finds a value for a numerical 
attribute in the checked file outside of this interval, 
a warning would be printed to the user indicating the violating value, 
the attribute, and the upper or lower Hampel threshold.

>>>>

We now describe a formalism how to compute the set of learned
probabilistic rules, denoted by $\mathcal{PR}$.
With $\mathcal{U}$ we denote a set of configuration files in the 
intermediate representation. If a template can be instantiated with
keywords from file $f$ and the obtained rule $r$ holds, we state that with the predicate 
$\mathit{appears}(r,f)$.
If a template is instantiated and we obtain rule $r$, with  the predicate 
$\mathit{holds}(r,f)$ we state that either $\mathit{appears}(r,f)$ holds, or $r$ could not be instantiated with keywords from $f$. With every 
rule $r$ we define two sets:
\begin{align*}
S_A(r)& =\{ \ f \in \mathcal{U}\ | \ \mathit{appears}(r,f)\  \} \\
S_H(r)& =\{ \ f \in \mathcal{U}\  | \ \mathit{holds}(r,f) \ \}
\end{align*}
We define then set $\mathcal{PR}$ as
$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)| > T_2 \ \} $$
where $T_1$ is a threshold value for considering rules which are true in 
majority of cases, and $T_2$ is a threshold value for considering rules 
for which we have at least some examples that that rule is will 
appear in the files. Finding the exact values of $T_1$ and $T_2$ is 
and their connection to $|\mathcal{U}|$
is a question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $T_1$ and $T_2$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.

Note that this approach differs from a unsupervised learning setting~\cite{hastie2009unsupervised} where the training set is completely unlabeled and seeks to discover some hidden underlying structure.
Although our set is also unlabeled, we make the assumption that some majority of the training set must be correct.% for their biggest part.
We are again learning a model which will provide clear justification (error locations) for the classification.
However, with this approach we will not have the formal guarantees of the ConfigC approach.
From previous work, we believe this is a worthwhile trade-off in order to decrease the false positive rate.

@@

In addition to checking for correlation, type, or ordering errors, 
the user may also want to examine if there are anomalous values that 
a keyword is assigned to. Such errors may also cause tricky and critical performance issues that are hard to debug.
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.

We now describe a technique that we plan to 
explore to detect anomalous values for 
numerical attributes. Let $A$ be the set of attributes contained in the 
configuration files in the sample dataset. 
Let $A_n$ be the subset of attributes of $A$ which are numerically typed. 
Then, for each attribute $a \in A_n$, we construct a vector $v_a$ of the 
values corresponding to attribute $a$, seen over the entire sample dataset.
For each $v_a$, we compute 
an interval  $$[\hat{v_a} - 50*MAD(v_a), \hat{v_a} + 50*MAD(v_a)],$$ 
where $\hat{v_a}$ represents the median over the values 
in $v_a$ and $MAD(v_a$) refers to the 
median absolute deviation. 
This is a variant of a standard outlier detection test, namely the Hampel identifier. (Mathematically, $MAD(v_a) = 1.4826* median(|v_a - \hat{v_a}|)$, estimating standard deviation 
for a normal distribution.) 
In the checking phase, if the checker finds a value for a numerical 
attribute in the checked file outside of this interval, 
a warning would be printed to the user indicating the violating value, 
the attribute, and the upper or lower Hampel threshold.
